```{python echo=FALSE}
import warnings
import pandas as pd
import numpy as np
import python.api_calls as api
import python.connectivity_assess as conn_table

warnings.filterwarnings('ignore')


```

```{r echo=FALSE}
#| echo: false
#| include: true
#| warning: false

library(reticulate)

```

# Connectivity Status Results {-}

## Current Connectivity Status {-}

In the Maqmekwitk watershed, X km of Plamu habitat are currently connected to the ocean and X km are disconnected from it. This means that X% of the X km of total habitat is connected.

In the Maqmekwitk watershed, X km of Kataq habitat are currently connected to the ocean and X km are disconnected from it. This means that X% of the X km of total habitat is connected.

## Structure Count {-}

In the Maqmekwitk watershed, X structures potentially disconnect Plamu habitat. Of these, X are identified as barriers in need of rehabilitation (priority barriers), X are identified as barriers that do not warrant rehabilitation (non-actionable), and X require further field assessment.

In the Maqmekwitk watershed, X structures potentially disconnect Kataq habitat. Of these, X are identified as barriers in need of rehabilitation (priority barriers), X are identified as barriers that do not warrant rehabilitation (non-actionable), and X require further field assessment.

## Maps {-}

![Figure 1: : Map of Plamu habitat and structures that are confirmed or potential barriers to fish passage in the Maqmekwitk watershed as of May 2026. Structure data were obtained from NSFishPass and the Canadian Aquatic Barriers Database (aquaticbarriers.ca). The accessibility model represents areas of the watershed that Plamu could access naturally in the absence of anthropogenic barriers. The habitat model represents the subset of accessible waterbodies that may be used by Plamu for spawning and rearing. Available local knowledge and data were incorporated and overruled habitat model results. Thick orange lines represent partially disconnected habitat (upstream of a partial barrier), and thick red lines represent habitat considered to be fully disconnected (upstream of barriers or unassessed structures). <br> A](images/Figure 1.png){fig-cap-location="top"}
 
![Figure 2: Map of Kataq habitat and structures that are confirmed or potential barriers to fish passage in the Stewiacke watershed as of May 2026. Structure data were obtained from the Canadian Aquatic Barriers Database (aquaticbarriers.ca). The accessibility model represents areas of the watershed that Kataq could access naturally in the absence of anthropogenic barriers. The habitat model represents the subset of accessible waterbodies that may be used by Kataq for growth and feeding. Available local knowledge and data were incorporated and overruled habitat model results. Thick orange lines represent partially disconnected habitat (upstream of a partial barrier), and thick red lines represent habitat considered to be fully disconnected (upstream of barriers or unassessed structures).<br> A](images/Figure 2.png){fig-cap-location="top"}

## Habitat Accumulation Curves

![Figure 3: Habitat Accumulation Curve (HAC) showing structures in the Maqmekwitk watershed that potentially block Plamu habitat, as of May 2026. Structures are ranked based on how much (km) weighted habitat for Plamu is upstream. The y-axis represents the cumulative amount of potential habitat gain (km), down-weighted by 75% for first-order streams and 25% for second-order streams, and by passability (25%, 50%, or 75%) of partial barriers. Sets of structures are indicated by a grey line below the curve, indicating that gains from addressing the downstream structure alone would be less than the combined gains from addressing all structures in the set. Habitat upstream of unassessed structures is considered disconnected until field assessments are completed. Structures that were excluded as passable are not shown. ](images/Figure 3.png){fig-cap-location="top"}

![Figure 4: Habitat Accumulation Curve (HAC) showing structures in the Maqmekwitk watershed that potentially block Kataq habitat, as of May 2026. Structures are ranked based on how much (km) weighted habitat for Kataq is upstream. The y-axis represents the cumulative amount of potential habitat gain (km), down-weighted by 75% for first-order streams and 25% for second-order streams, and by passability (25%, 50%, or 75%) of partial barriers. Sets of structures are indicated by a grey line below the curve, indicating that gains from addressing the downstream structure alone would be less than the combined gains from addressing all structures in the set. Habitat upstream of unassessed structures is considered disconnected until field assessments are completed. Structures that were excluded as passable are not shown. ](images/Figure 4.png){fig-cap-location="top"}

## Habitat Accumulation Summary Table

```{r hac1, echo = FALSE, results = 'asis'}
#| label: table-1
#| tbl-cap: "Table 1.  Labelled structures in the Habitat Accumulation Curve (Figure 3 and 4), their rank, and weighted upstream habitat for Plamu and Kataq in Maqmekwitk watershed. Habitat gain (averaged across sets) represents the amount (km) of weighted habitat upstream of that structure to the next structure and depicts the potential gain in habitat if passage at that structure was restored. "
#| warning: false
#| echo: false
source("Rscripts/table_formatting.R")
library("flextable")

data <- read.csv("data/table1.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

```{r hac2, echo = FALSE, results = 'asis'}
#| label: table-2
#| tbl-cap: "Table 2. Labelled structures in the Habitat Accumulation Curve (Figure 4), their rank, and weighted upstream habitat for American Eel in the Stewiacke watershed. Weighted Habitat Gain per Set represents the amount (km) of weighted habitat upstream of that structure to the next structure and depicts the immediate potential gain in habitat if passage at that structure was restored. Total Weighted Habitat Upstream per Set (km) represents the total amount (km) of weighted habitat upstream of the set, regardless of upstream structures, and depicts the long-term potential gain in habitat if passage at that structure (and all other upstream structures) was restored. Structure rank represents the model ranking of all sets of 1 or more structures."
#| warning: false
#| echo: false
source("Rscripts/table_formatting.R")
library("flextable")

data <- read.csv("data/table2.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```